%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {Ezoic} % Organization
    {Carlsbad, CA} % Location
    {March 2020 - July 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Code Development:} Regularly designed and developed high-quality, scalable code for various systems, focusing on improving functionality and user experience.}
        \item {\textbf{Mentorship:} Acted as a mentor to junior developers, guiding them through complex software development cycles and fostering a culture of technical excellence and innovation.}
        \item {\textbf{Cross-Functional Collaboration:} Worked closely with other teams, including sales and account management, to understand client needs and translate them into functional software solutions. Facilitated technical discussions and decision-making processes that aligned with strategic business objectives.}
        \item {\textbf{Domain Expertise:} Maintain and enhance core JavaScript integrations, providing deep technical knowledge and support.}
        \item {\textbf{Strategic Contributions:} Participated the annual strategic planning process, researching market trends, competitor analysis, and emerging technologies to inform strategic directions and company positioning.}
        \item {\textbf{Technical Support:} Provided critical support to account managers and clients, addressing technical queries and troubleshooting issues to enhance customer satisfaction and service delivery.}
        \item {\textbf{Recruitment:} Actively participated in final interviews during intense hiring periods, helping to select and onboard top-tier talent.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
